
% Preamble
% -----------------------------------------------------------------

\documentclass{article}

% Packages
% -----------------------------------------------------------------

%\usepackage{amsmath}                    % Advanced math typesetting
%\usepackage [utf8] {inputenc}       % Unicode support (Umlauts etc)
%\usepackage [ngerman] {babel}             % Change hyphenationrules
%\usepackage{hyperref}                 % Add a link to your document
%\usepackage{graphicx}                % Add picturesto your document
%\usepackage{listing}      % Source Code formatting and highlighting
%\usepackage{enumitem}                  % Used for enumeration-lists

% Document Info
% -----------------------------------------------------------------

\author{Ty Yiu}                                 % The author's name
\title{Activity One}           % The title of the document
\date{27 September 2018}
\begin{document}
\maketitle                                        % Generates title 
%
% \tableofcontents{}                  % Generates table of contents 
                                    % from sections and subsections

% Commands
% -----------------------------------------------------------------

%\section{}                                          % Section Title

% --------------------

%\subsection{}                                    % Section Title XS

% --------------------

%\subsubsection{}                                % Section Title XXS

% --------------------

%\paragraph{}                                      % Paragraph Title

% --------------------

%\subparagraph{}                                % Subparagraph Title

% --------------------

%\begin{itemize}                                 % Unenumerated List
%\item ITEM
%\item ITEM
%\item ITEM
%\item ITEM
%\end{itemize}
 
% --------------------

%\begin{enumerate}                         % Enumerated List (1.2.3.)
%\item ITEM
%\item ITEM
%\end{enumerate}

% --------------------

%\begin{enumerate}                         % Enumerated List (1.2.3.)
%\item ITEM                    % With Nested List with Items (a.b.c.)
%\begin{enumerate}
%\item ITEM
%\item ITEM
%\end{enumerate}
%\item ITEM
%\end{enumerate}

% --------------------    

%\textit{}                                              % Italic Text

% --------------------

%\textbf{}                                                 % Bold Text

% --------------------


Analyze the dilemma in the following scenario from the vantage point of both utilitarian and deontological ethical theories.
 In particular, how might Ross’s theory of act-deontology apply?

\medskip
The United States government, with the approval of the majority of Americans, has decided to round up all Arab-Americans and relocate them into internment camps.
 You have a friend who is an American citizen of Arab descent.
 She asks you to protect her from the authorities.
 You have known this person all of your life, and you are convinced that she is a loyal American.
 So you agree to hide her in the third your of your house.
 Next, imagine that a United States federal agent knocks on your door and asks if you know the whereabouts of the person you are hiding.
 How would you respond to that agent?

\medskip
You realize that you cannot both keep your promise to your friend and tell the truth to the federal agent.
 Initially, your gut reaction might suggest that the solution to your dilemma is really quite simple: a far greater good will be served by lying to the federal agent than by breaking your promise to your friend.
 However, to embrace the moral principle underlying that line of reasoning is to embrace a form of utilitarianism.
 And we have already seen some of the difficulties that can result from trying to be a consistent and thoroughgoing utilitarian.

\medskip
Furthermore, could you consistently universalize a moral principle that states: Whenever you must choose between telling the truth to authorities and breaking a promise to a friend, you should always keep your promise?
Will that principle always work?
\smallskip
Write a short answer to the above questions (no more that an A4 page long)


\end{document}
